\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper}
\usepackage{graphicx}
\usepackage{hyperref}

\title{
    Software Requirements Specification for Analytics-Driven SEO \& SEA Optimization\\[1ex] % Title
    \author{Svetoslav Stoyanov\\Student Number: 3793222}
    \date{Internship Period: February 2024 - June 2024}
    \large Spienzer B.V.\\ % Company Name
    \large Fontys University of Applied Sciences, Venlo\\03.03.2024 % University Name
}
\begin{document}

\maketitle
\newpage % This command forces a new page

\section{Introduction}
This document outlines the requirements for developing a software system that integrates with Google Analytics to provide website and per-page analytics functionalities, generates a priority ranking algorithm for website optimization, and predicts web traffic per page.

\subsection{Product Perspective}
This software is designed for Spienzer B.V., a company specializing in SEO and SEA (Search Engine Optimization and Search Engine Advertising).

\subsubsection{Product Functions}
\begin{itemize}
    \item Integrate with Google Analytics to access relevant data.
    \item Correlate search volume, SERP (Search Engine Results Page) position, and web traffic data for each webpage.
    \item Provide a user interface (frontend) for website and per-page analytics visualization.
    \item Implement a backend system to process and store data.
    \item Develop an algorithm to prioritize pages needing optimization based on integrated data.
    \item Develop an algorithm to predict potential number of visitors per webpage.
\end{itemize}

\subsection{User Characteristics}
The primary users are marketing employees, particularly those in the IT and SEO/SEA departments.
Concrete user groups, personas and user stories to be created.
\subsection{General Constraints}
\begin{itemize}
    \item The system should be compatible with major web browsers and operating systems.
    \item Performance and scalability should be sufficient to handle the expected data volume.
    \item Security measures should be implemented to protect sensitive data.
\end{itemize}

\section{Specific Requirements}
\subsection{Functional Requirements}
\subsubsection{Google Analytics Integration}
The system shall seamlessly integrate with the Google Analytics API.

\subsection{Non-Functional Requirements}
\subsubsection{Performance}
The system should be able to handle real-time data updates efficiently.

\section{Design Constraints}
\subsection{Hardware and Software Interfaces}
The system should be compatible with Spienzer's existing infrastructure and software tools.
\newpage % Assuming you want the word count on a new page or adjust placement as needed
\section*{Document Metadata}
\textbf{Word Count}: XXXX words.

\end{document}
